CdGF_aucrf

### 2016-09-26 code/CdGF_AUCRF.Rmd
fix aucrf legend

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_euth_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10f_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOO_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcO_roc, col='purple', lwd=2, add=T, lty=3)
plot(ran_cv10f_roc, col='orange', lwd=2, add=T, lty=1)
plot(predict_random_roc, col='red', lwd=2, add=T, lty=3)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_euth_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOO_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcO_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10f_roc$auc),
                               sprintf('Random (AUC: %.3g)',ran_cv10f_roc$auc),
                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_euth_roc,LOO_roc)$p.value),
                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_euth_roc,cv10f_roc)$p.value)
),lty=c(1,2,2,1,3,0,0), lwd=2, col=c('black','blue','red','gray','orange'), bty='n')
```

>>>>

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_euth_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10f_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOO_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcO_roc, col='purple', lwd=2, add=T, lty=3)
plot(ran_cv10f_roc, col='orange', lwd=2, add=T, lty=1)
plot(predict_random_roc, col='red', lwd=2, add=T, lty=3)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_euth_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOO_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcO_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10f_roc$auc),
                               sprintf('Random OOB (AUC: %.3g)',predict_random_roc$auc),
                               sprintf('Random 10-fold CV (AUC: %.3g)',ran_cv10f_roc$auc),
                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_euth_roc,LOO_roc)$p.value),
                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_euth_roc,cv10f_roc)$p.value)
),lty=c(1,2,2,1,3,1,0,0), lwd=2, col=c('black','blue','purple','gray','red','orange'), bty='n')
```
